---
title: "Notes"
author: "Yuege Zhang"
date: "4/9/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Types of Data Analysis
1. Descriptive   
Goal: Describe or summarize a set of data  
- Early analysis when receive new data   
- Generate simple sumamries about the samples and their mesurements  
- Not forgeneralziing the results of the analysis to a larger population or trying to make conclusions  
e.g: mean, median, mode, range, sd, variance, scatter plot, histogram etc.    
2. Exploratory  
Goal: Examine the data and find relationships that weren't previously known  
- Explore how different variables might be related  
- Useful for discovering new connections  
- Help to formulate hypotheses and drive the design of future sudies and data collection    
e.g: correlation   
Tell us the there exits relationship, not the cause.
3. Inferential    
Goal: Use a relatively small sample of data to say something about the population at large   
- Provide your estimate of the variable for the population and provide your uncertainty about your estimate   
- Ability to accurately infer information about the larger population depends heavily on sampling scheme    
4. Predictive
Goal: Use current and historical data to make predictions about future data  
- Accuracy in predictions is dependent on measuring the right variables   
- Many ways to build up prediction model with some being better or worse for specific cases   
5. Causal
Goal: See what happens to one variable when we manipulate another variable  
- Gold Standard in data analysis  
- Often applied to the results of randomized studies that were designed to identify causation   
- Usually analyzed in aggregate and observed relationships are usually average effects   
6. Mechanistic
Goal: Understand the exact changes in variables that lead to exact changes in other variables
- Applied to simple situations or those that are nicely modelded by deterministic equations   
- Commonly applied to physical or engineering sciences   
- Often the only noise in the data is measurement error   


# Experimental Design
Steps:
1. Formulate your question  
2. Designing your experiment
3. Identify problems and sources of error
Confounder: 第三干扰因素
4. Collect the data   
Methods:
-Blinded: Subjects don't know which group(Control,Treatment) they are in. 
  -Randomization & Replication to remove confounders

# Read and Output Data
```{r}
x= "aaa"
y= data.frame(a=1,b="3a")
dump(c("x","y"),file="data.R")
rm(x,y)
source("data.R")
y
x
```

# Subsetting Lists
```{r}
x=list(foo=1:4,bar=0.6)
str(x)
str(x[1])
str(x[[1]])
str(x$foo)
```

# Subsetting a Matrix
```{r}
x=matrix(1:6,2,3)
str(x)
str(x[1,2])
str(x[1,2,drop=FALSE])
```

# Partial Matching
```{r}
x=list(dfsefsef=1:5)
x$d
x[["d"]]
x[["d",exact=FALSE]]

```

# Removing NA Values
```{r}
x=c(1,2,NA,4,NA,5)
bad=is.na(x)
x[!bad]
y=c("a","b",NA,"d","e",NA)
good=complete.cases(x,y)
good
x[good]
y[good]


```












